---
title: "R code for analysis of covid fishing data"
author: "Carl Smith"
date: "2022-09-06"
output: html_document
---
    
## Libraries
    
```{r message=FALSE}
# Clear all and restart
# rm(list = ls())
# .rs.restartR()

# setwd("~/Documents/1. TO DO/Lithuania/CovidFish")

#Load packages
library(arm)
library(car)
library(ggplot2)
library(lattice)
library(lawstat)
library(outliers)
library(tidyverse)
library(lme4)
library(car)
library(lmerTest)
library(MuMIn)
library(performance)
library(sjPlot)
library(sjmisc)
library(sjlabelled)
library(gridExtra)
library(GGally)
library(plyr)
library(glmmTMB)
library(DHARMa)
library(lubridate)
library(aweek)
library(zoo)
library(rio)
# library(INLA)
# library(inlatools)
# library(brinla)
```

## Data

```{r}

######################################
#Import the Czech data into dataframe 'dfD'
# dfD <- readRDS("Ddaily_new10.rds")
# dfD <- readRDS("Ddaily_water.rds")

dfD <- import(here::here("data", "plots","Ddaily_new10.rds" ))

str(dfD)
names(dfD)

# [1] "date_name"              "municipality"           "anglers_per_day"       
# [4] "workplace_closures"     "school_closures"        "stay_home_requirements"
# [7] "n_unique_day"           "day_of_week"            "weekend"               
# [10] "pop_2018"               "pop_2019"               "pop_2020"              
# [13] "pop_2021"   
```

## Setting alternative lockdown dates

```{r}
# #checking lockdown values
# firstmuni <- first(unique(tt2$municipality))
# oneMuni <- dfD %>% filter (municipality == firstmuni) %>% filter (date_name > "2019-12-31")
# tt2 <- which(oneMuni$date_name > "2020-03-10" & oneMuni$date_name < "2020-05-31")
# 
# ## replace with new values
# dfDe <- dfD
# dfDe$stay_home_requirements <- 0
# dfDe$stay_home_requirements[which(dfDe$date_name > "2020-03-10" & dfDe$date_name < "2020-05-31")] <- 1
# dfDe$stay_home_requirements[which(dfDe$date_name > "2020-10-23" & dfDe$date_name < "2021-05-20")] <- 1
# 
# dfDoriginal <- dfD
# dfD <- dfDe
```

##Data exploration

```{r}
# Are there missing values?
colSums(is.na(dfD))

# OUTLIERS

# Define preferred figure format
My_theme <- theme(axis.text.y = element_blank(),
                  axis.ticks.y = element_blank(),
                  axis.ticks.x=element_blank(),
                  panel.background = element_blank(),
                  panel.border = element_rect(fill = NA, size = 1),
                  strip.background = element_rect(fill = "white", 
                                                  color = "white", size = 1),
                  text = element_text(size = 14),
                  panel.grid.major = element_line(colour = "white", size = 0.1),
                  panel.grid.minor = element_line(colour = "white", size = 0.1))

# A function for dotplots
multi_dotplot <- function(filename, Xvar, Yvar){
  filename %>%
    ggplot(aes(x = {{Xvar}})) +
    geom_point(aes(y = {{Yvar}})) +
    theme_bw() +
    coord_flip() +
    labs(x = "Order of Data")}


# Are data balanced among levels of the categorical covariates?
count(dfD$municipality)
#96 levels

table(dfD$workplace_closures)
# 0     1     2     3 
# 85344 14304 47616  4512 

table(dfD$school_closures)
# 0      1     2     3 
# 87360 31584 18528 14304 

table(dfD$stay_home_requirements)
# 0     1 
# 111360  40416 

table(dfD$day_of_week)
# Sun  Mon   Tue   Wed   Thu   Fri   Sat 
# 21600 21696 21696 21696 21696 21696 21696 

table(dfD$weekend)
# yes    no 
# 43296 108480 

dfD$year  <- year(dfD$date_name)
table(dfD$year)
# 2018  2019  2020  2021  2022 
# 35040 35040 35136 35040 11520 

dfD$month <- month(dfD$date_name)
table(dfD$month)
# 1     2     3     4     5     6     7     8      9     10     11   12 
# 14880 13536 14880 14400 11904 11520 11904 11904 11520 11904 11520 11904 

# Create variable 'lock' indicating level of lockdown
dfD$lock <- dplyr::recode(dfD$stay_home_requirements,
                         "0" = "no",
                         "1" = "yes")
dfD$lock <- as.factor(dfD$lock)


table(dfD$lock)
# no    yes 
# 111360  40416 


#CALCULATE NUMBER OF ZEROS IN THE RESPONSE VARIABLES

# What is the percentage of zeros for anglers_per_day?

sum(dfD$anglers_per_day == 0)
# 137279 zeros

round(sum(dfD$anglers_per_day == 0) * 100 / nrow(dfD),0)
# 95% zeros - potential risk of zero-inflation


#NORMALITY AND HOMOGENEITY OF DEPENDENT VARIABLE(S)

# Frequency polygon plot
dfD %>% ggplot(aes(anglers_per_day)) +
  geom_freqpoly(bins = 15) +
  labs(x = "anglers_per_day", y = "Frequency") +
  My_theme +
  theme(panel.border = element_rect(colour = "black", 
                                    fill=NA, size = 1))

#COLLINEARITY
# Calculate VIF (for glm)
round(vif(glm(anglers_per_day ~ weekend * lock,
                          family = poisson(link = "log"),
                          data = dfD)),1)
#  weekend         lock weekend:lock 
# 1.7          1.8          2.5 

# create variable 'pop' in each year as single column
df18 <- dplyr::select(filter(dfD, year == 2018), 
               c(date = date_name, muni = municipality, apd = anglers_per_day, 
                 unique = n_unique_day, day = day_of_week, weekend, pop = pop_2018,
                 lock, month, year))

df19 <- dplyr::select(filter(dfD, year == 2019), 
               c(date = date_name, muni = municipality, apd = anglers_per_day, 
                 unique = n_unique_day, day = day_of_week, weekend, pop = pop_2019,
                 lock, month, year))

df20 <- dplyr::select(filter(dfD, year == 2020), 
               c(date = date_name, muni = municipality, apd = anglers_per_day, 
                 unique = n_unique_day, day = day_of_week, weekend, pop = pop_2020,
                 lock, month, year))

df21 <- dplyr::select(filter(dfD, year == 2021), 
               c(date = date_name, muni = municipality, apd = anglers_per_day, 
                 unique = n_unique_day, day = day_of_week, weekend, pop = pop_2021,
                 lock, month, year))

df22 <- dplyr::select(filter(dfD, year == 2022), 
                      c(date = date_name, muni = municipality, apd = anglers_per_day, 
                        unique = n_unique_day, day = day_of_week, weekend, pop = pop_2021,
                        lock, month, year))

dfD1 <-rbind(df18, df19, df20, df21, df22)
names(dfD1)
rm(df18, df19, df20, df21, df22)

#PLOT RELATIONSHIPS

# Plot response variable against covariates
# And check change in no. sonar devices and pop size with year
par(mfrow=c(2,2), mar=c(5,5,1,1), cex.lab = 1)
plot(apd ~ pop,  data = dfD1,
     xlab = "pop", 
     ylab = "apd",
     pch = 16, cex = 1.3)
boxplot(apd ~ weekend, data = dfD1, 
        xlab = "weekend", 
        ylab = "apd",
        range = 0,
        pch = 16, cex = 1.3, col = "blue")
boxplot(apd ~ lock, data = dfD1, 
        xlab = "lock", 
        ylab = "apd",
        range = 0,
        pch = 16, cex = 1.3, col = "green")
boxplot(unique ~ year, data = dfD1, 
        xlab = "year", 
        ylab = "unique",
        range = 0,
        pch = 16, cex = 1.3, col = "red2")
```

## Question
Did covid lockdown increase number of anglers per day?
(after adjusting for region, year, season, and
controlling for temporal changes in the number of sonar devices)
Also include weekend vs weekday as a fixed factor and interactions with lockdown

## Some data wrangling/housekeeping

```{r}

# Create new variable 'season'
dfD1$season <- dplyr::recode(dfD1$month,
                           "12" = "winter", 
                           "1"  = "winter", 
                           "2"  = "winter", 
                           "3"  = "spring", 
                           "4"  = "spring", 
                           "5"  = "spring", 
                           "6"  = "summer", 
                           "7"  = "summer",
                           "8"  = "summer",
                           "9"  = "autumn",
                           "10" = "autumn",
                           "11" = "autumn")

table(dfD1$season)
# autumn spring summer winter 
# 34944  41184  35328  40320 

# Standardize continuous covariates to avoid numerical problems
dfD1$uni.std <- (dfD1$unique-mean(dfD1$unique))/sd(dfD1$unique)
dfD1$pop.std <- (dfD1$pop-mean(dfD1$pop))/sd(dfD1$pop)

# Create variable for phase of covid pandemic
dfD1 <- dfD1[dfD1$date > "2017-12-31" &
               dfD1$date < "2022-01-01", ]

# dfD1 <- dfD1 %>%
#   mutate(phase = case_when(
#     between(date, as.Date("2017-12-31"), as.Date("2020-04-24")) ~ "Pre",
#     between(date, as.Date("2020-04-25"), as.Date("2020-10-20")) ~ "During1",
#     between(date, as.Date("2020-10-21"), as.Date("2020-11-08")) ~ "Post1",
#     between(date, as.Date("2020-11-09"), as.Date("2021-05-20")) ~ "During2",
#     # Note a brief break from lockdown from 2020-11-16 to 2020-11-22
#     between(date, as.Date("2021-05-21"), as.Date("2022-01-01")) ~ "Post2")
#   )

### or alternative days
#dfDe$stay_home_requirements[which(dfDe$date_name > "2020-03-10" & dfDe$date_name < "2020-05-31")] <- 1
#dfDe$stay_home_requirements[which(dfDe$date_name > "2020-10-23" & dfDe$date_name < "2021-05-20")] <- 1

dfD1 <- dfD1 %>%
  mutate(phase = case_when(
    between(date, as.Date("2017-12-31"), as.Date("2020-03-09")) ~ "Pre",
    between(date, as.Date("2020-03-10"), as.Date("2020-05-31")) ~ "During1",
    between(date, as.Date("2020-06-01"), as.Date("2020-10-23")) ~ "Post1",
    between(date, as.Date("2020-10-24"), as.Date("2021-05-20")) ~ "During2",
    # Note a brief break from lockdown from 2020-11-16 to 2020-11-22
    between(date, as.Date("2021-05-21"), as.Date("2022-01-01")) ~ "Post2")
  )


dfD1$phase <-as.factor(dfD1$phase)
dfD1$phase <- relevel(dfD1$phase, ref = "Post2")
dfD1$phase <- relevel(dfD1$phase, ref = "During2")
dfD1$phase <- relevel(dfD1$phase, ref = "Post1")
dfD1$phase <- relevel(dfD1$phase, ref = "During1")
dfD1$phase <- relevel(dfD1$phase, ref = "Pre")
table(dfD1$phase)

dfD1$weekend <- relevel(dfD1$weekend, ref = "no")

# Pre     During1   Post1   During2   Post2 
# 81120   17184     1824    18528     21600 
```

## Fit GLMM 

Include unique sonar devices as an offset (adjust for change in number of devices)
A high proportion of zeros (i.e. possible zero-inflation)
Start with Poisson
Include year and season as random intercept (with pop as random slope)
Examine interaction of lockdown phase with weekend

```{r}

# Poisson GLMM
poisson1 <- glmmTMB(apd ~ phase * weekend + pop.std + uni.std +
                          (1|year) + (1|season) + (1|muni),
                          family = poisson(link = "log"),
                          ziformula=~0,
                          data = dfD1)
#saveRDS(poisson1, file = "poisson1DenmarkEd.rds")

check_overdispersion(poisson1)   # 0.97 - not overdispersed

# Simulate data using model parameters
SimPois <- simulateResiduals(fittedModel = poisson1, plot = F)

# Use simulated data to test zero-inflation
par(mfrow=c(1,1), mar=c(5,5,1,1), cex.lab = 1)
testZeroInflation(SimPois)
# No problem with zero-inflation

# Deal with overdispersion with a negative binomial (linear) model
nbinom1 <- glmmTMB(apd ~ phase * weekend + pop.std + uni.std +
                         (1|year) + (1|season) + (1|muni),
                         family = nbinom1(link = "log"),
                         ziformula=~0,
                         data = dfD1)
#saveRDS(nbinom1, file = "nbinom1DenmarkEd.rds")

# Compare  models with AIC
round(AIC(poisson1, nbinom1),0)

#          df  AIC
# poisson1 15 49933
# nbinom1  16 49832

#new data (edited dates)
#          df   AIC
# poisson1 15 49928
# nbinom1  16 49828

check_overdispersion(nbinom1)  #0.92 No overdispersion detected
##ASKCarl: #Error: Model must be from Poisson or binomial family.

# Simulate data using model parameters
SimNB1 <- simulateResiduals(fittedModel = nbinom1, plot = F)

# Examine zero-inflation
par(mfrow=c(1,1), mar=c(5,5,1,1), cex.lab = 1)
testZeroInflation(SimNB1)
# No problem with zero-inflation

# Model 'nbinom1' is the best-fitting model that is not overdispersed
```

## MODEL VALIDATION

```{r}
#Obtain residuals and fitted values
Res <- resid(nbinom1)
Fit <- fitted(nbinom1)

# Plot residuals against fitted values
par(mfrow = c(2,3), mar = c(5,5,2,2))
plot(x = Fit,
     y = Res,
     xlab = "Fitted values",
     ylab = "Residuals",
     pch = 16, cex = 1.5)
abline(h = 0, lty = 2)
abline(v = 0, lty = 2)

# Plot the residuals vs pop
plot(x = dfD1$pop.std,
     y = Res,
     xlab = "population size",
     ylab = "Residuals",
     pch = 16, cex = 1.5)
abline(h = 0, lty = 2)
abline(v = 0, lty = 2)

boxplot(Res ~ phase, 
        xlab = "phase",
        ylab = "Residuals",
        range = 0,
        data = dfD1)
abline(h = 0, lty = 2)

# Plot the residuals vs weekend
boxplot(Res ~ weekend, 
        xlab = "weekend",
        ylab = "Residuals",
        range = 0,
        data = dfD1)
abline(h = 0, lty = 2)

# Plot the residuals vs season
boxplot(Res ~ season, 
        xlab = "season",
        ylab = "Residuals",
        range = 0,
        data = dfD1)
abline(h = 0, lty = 2)

# Plot the residuals vs year
boxplot(Res ~ year, 
        xlab = "year",
        ylab = "Residuals",
        range = 0,
        data = dfD1)
abline(h = 0, lty = 2)

par(mfrow = c(1,1), mar = c(5,5,2,2))
boxplot(Res ~ muni, 
        xlab = "muni",
        ylab = "Residuals",
        range = 0,
        data = dfD1)
abline(h = 0, lty = 2)


# Use 'check_model'
# check_model(nbinom1)
```

##Plotting model results 

```{r}
# Plotting theme
My_theme <- theme(panel.background = element_blank(),
                  panel.border = element_rect(fill = NA, 
                                              color = "black", size = 1.4),
                  strip.background = element_rect(fill = "NA", 
                                                  color = "white", size = 1),
                  text = element_text(size = 14),
                  panel.grid.major = element_line(colour = "white", size = 0.1),
                  panel.grid.minor = element_line(colour = "white", size = 0.1))

# Plot fixed effects
set_theme(
  base = theme_bw(),
  axis.textsize = 1)
plot_model(nbinom1,
           vline.color = "green4", 
           sort.est = FALSE,
           title = "Denmark",
           show.zeroinf = T,
           show.values = TRUE)

# Random effects
set_theme(
  base = theme_bw(),
  axis.textsize = 1)
plot_model(nbinom1,
           show.zeroinf = T,
           vline.color = "green4",
           title = "Denmark",
           type = "re")

# Define preferred figure format
My_theme <- theme(panel.background = element_blank(),
                  panel.border = element_rect(fill = NA, size = 1),
                  strip.background = element_rect(fill = "white", 
                                                  color = "white", size = 1),
                  text = element_text(size = 14),
                  panel.grid.major = element_line(colour = "white", size = 0.1),
                  panel.grid.minor = element_line(colour = "white", size = 0.1))

plot_model(nbinom1,
           type = "pred", 
           terms = c("pop.std", "weekend", "phase"),
           colors = c("blue", "firebrick2"),
           show.data = F,
           pred.type = c("fe"),
           title = "",
           axis.title = c("Standardised population size", 
                          "SB users / day / municipality"),
           show.legend = FALSE,
           show.values = F) + My_theme +
  scale_y_continuous(limits = c(0, 0.3)) + 
  scale_x_continuous(limits = c(-0.25, 2.25))


# Model summary
summary(nbinom1)

#Summarise neatly
tab_model(nbinom1,
          show.zeroinf = F,
          # pred.labels = c("Intercept", "Weekend (Yes)", "Phase (Dur)", "Phase (Post)",
          #                 "Weekend (Yes): Phase (Dur)", "Weekend (Yes): Phase (Post)"),
          dv.labels = c("Negative binomial GLMM (Danish data)"),
          string.pred = "Coefficient",
          string.ci = "Conf. Int (95%)",
          string.p = "P-value",
          p.style = c("numeric"),
          emph.p = FALSE,
          transform = NULL,
          file = "DenmarkFinal.doc")

###############################

# Plot model
round(range(dfD1$pop.std),2)

MyData <- expand.grid(
  phase = levels(dfD1$phase),
  weekend = levels(dfD1$weekend),
  pop.std = seq(-0.8,6, length = 25),
  uni.std = 0)
head(MyData)
tail(MyData)

X <- model.matrix(~ phase * weekend + pop.std + uni.std, data = MyData)

#Calculate predicted values
MyData$eta  <- X %*% fixef(nbinom1)$cond
MyData$Pred <- exp(X %*% fixef(nbinom1)$cond)

#Calculate standard errors (SE) for predicted values
MyData$SE    <- sqrt(diag(X %*%vcov(nbinom1)$cond %*% t(X)))
MyData$SeUp  <- exp(MyData$eta + 1.96 *MyData$SE) 
MyData$SeLo  <- exp(MyData$eta - 1.96 *MyData$SE) 

#Back-standardize population size to natural scale
MyData$pop <- (MyData$pop.std * sd(dfD1$pop) + mean(dfD1$pop))/10000

# Set theme
My_theme <- theme(panel.background = element_blank(),
                  panel.border = element_rect(fill = NA, color = "black", size = 1.4),
                  strip.background = element_rect(fill = "NA", 
                                                  color = "white", size = 1),
                  text = element_text(size = 11, colour = "black"),
                  panel.grid.major = element_line(colour = "white", size = 0.1),
                  panel.grid.minor = element_line(colour = "white", size = 0.1))


# Add labels
label_phase <- c(Pre = "Pre lockdown", 
                 During1 = "Lockdown 1",
                 Post1 = "Post lockdown 1", 
                 During2 = "Lockdown 2", 
                 Post2 = "Post lockdown 2")

# Plot
DenmarkEditedDates <- ggplot(MyData, aes(x = pop, y = Pred, group = weekend, fill = weekend)) +
  ggtitle("Denmark") +
  theme(plot.title = element_text(hjust = 0.5))+
  # geom_jitter(data = dfD1,
  #             aes(y = apd, x = (pop/10000), group = weekend, col = weekend),
  #             shape = 16, size = 0.5,
  #             height = 0.5, width = 30, alpha = 0.2) +
  xlab("Population size (tens of thousands)") + 
  ylab("Sonar buoy users per day per municipality") +
  ylim(0,2) + xlim(0,50) +
  theme(plot.title = element_text(face="bold", size=14))+
  theme(text = element_text(size = 13)) +
  theme(panel.background = element_blank())+
  theme(panel.border = element_rect(fill = NA, colour = "black", size = 1))+
  theme(strip.background = element_rect
        (fill = "white", color = "white", size = 1))+
  geom_line(data = MyData, aes(x = pop, y = Pred, color = weekend, 
                               group = weekend), size = 1)+
  scale_color_manual(values=c("slateblue1", "firebrick1"), 
                     name="",
                     breaks=c("no", "yes"),
                     labels=c("Weekday", "Weekend"))+
  My_theme +
  geom_ribbon(data = MyData,aes(x = pop, ymax = SeUp, 
                                ymin = SeLo), alpha = 0.3)+
  scale_fill_manual(values=c("slateblue1", "firebrick1"), 
                    name="",
                    breaks=c("no", "yes"),
                    labels=c("Weekday", "Weekend"))+
  facet_grid(. ~ phase, scales = "fixed", space = "fixed",
             labeller=labeller (phase = label_phase)) +
  theme(strip.text = element_text(size = 12, face="italic")) +
  theme(legend.position = "bottom")

DenmarkEditedDates

#save(DenmarkEditedDates, file = "DenmarkPlot.RData")

```
